Disturbance-aware minimum-time planning strategies for motorsport vehicles with probabilistic safety certificates

### 2025-04-28 stochastic_vehicle_dynamics.tex
[MM] Stay-on-track constraint partial

\subsection{Robust adherence limit constraint formulation}
The model employs a tire formulation that neglects combined slip effects, i.e., it does not account for the simultaneous utilization of longitudinal and lateral tyre forces. As a result, the optimal control problem must include an additional constraint to ensure that the total ground reaction forces remain within the bounds of the tyre's adherence ellipse.

@@

>>>>

\subsection{Robust adherence limit constraint formulation}
\label{sec:adherence_constraint}
The model employs a tire formulation that neglects combined slip effects, i.e., it does not account for the simultaneous utilization of longitudinal and lateral tyre forces. As a result, the optimal control problem must include an additional constraint to ensure that the total ground reaction forces remain within the bounds of the tyre's adherence ellipse.

@@

\subsection{Stay-on-track constraint}
\label{sec:stayontrack_constraint}
A stay-on-track constraint is required to ensure that the vehicle remains within the circuit boundaries. The formulation adopted introduces an algebraic variable $e$, which satisfies the following constraint:
\begin{equation}
	\begin{Bmatrix}
		x\\y
	\end{Bmatrix}
	-\boldsymbol{c} - e\bn=\boldsymbol{0} \label{eq:onplane_constraint}
\end{equation}
%\begin{equation}
%	\bp-\boldsymbol{c}_k - e_k\bn_k=\boldsymbol{0} \label{eq:onplane_constraint}
%\end{equation}
where $\boldsymbol{c}$ indicates the position of the centerline, and $\bn$ is the unit normal vector to the centerline. Equation~\eqref{eq:onplane_constraint} constraints the CoM of the vehicle to lie on the vertical plane defined by the unit normal vector $\bn$. The previously introduced algebraic variable $e$ is further constrained to take values between $e_\textrm{min}$ and $e_\textrm{max}$, which are determined based on the width of the circuit and the vehicle's front and rear tracks.

In order to take into account for the back-off terms, the maximum and minimum values are modified coherently, so that:
\begin{equation}
	e_\textrm{min} + \be^\textrm{SOT} \leq e \leq e_\textrm{max} - \be^\textrm{SOT}\label{eq:stayontrack_constraint}
\end{equation}
where $\be^\textrm{SOT}$ is computed by considering that the gradient of the constraint w.r.t. the state vector $\na_{\bx}h^\textrm{SOT}$ depends solely on $\bn$.
%Adding a back-off to this constraint produces the same effect as an increase of the front and rear tracks of the vehicle does.
